Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-04 paper/main.tex
table

\renewcommand{\myparagraph}[1]{\smallskip{}\noindent\textbf{#1}.}

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}[]
\begin{tabular}{rrrrrrrrr}
\multicolumn{1}{c}{\textbf{}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{4}{c}{\textbf{Mean fitness (sd)}}                       & \multicolumn{1}{c}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}95\% CI of the \\ mean difference\end{tabular}}}} & \multicolumn{2}{c}{\textbf{Runtime}} \\ \cline{3-6} \cline{8-9} 
\textbf{Problem}              & \textbf{Instance}             & \multicolumn{2}{r}{\textbf{CEGO}} & \multicolumn{2}{r}{\textbf{UMM}} & \multicolumn{1}{c}{}                                                                                                    & \textbf{CEGO}     & \textbf{UMM}     \\ \hline

@@

PFSP                          & rec31                         & 3415.5           & (62.1)         & 3419.3          & (37.0)         & {[}-52.6, 45.0{]}                                                                                                       & 23.1              & 0.5             
\end{tabular}

@@

>>>>

\newcommand{\myparagraph}[1]{\smallskip{}\noindent\textbf{#1}.}

@@

\newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
\begin{table*}[tb]
  \caption{Mean fitness (and standard deviation) of the best solution found. % at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. 
  Mean runtime is shown in hours. 
  %CEGO runs were stopped after 144 hours. This was the case for all LOP instances.
  \label{tab:results}}
  \resizebox{\textwidth}{!}{%
\begin{tabular}{r@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}
 \toprule
            &              & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the                                                                                                                                                                                                                                                                                           \\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
\bf Problem & \bf Instance & \mcolc{2}{CEGO}              & \mcolc{2}{UMM}                                                                                                                                                                                                               &                                                          &           & \bf                       & \bf CEGO & \bf UMM \\\midrule

@@

PFSP        & rec31        & 3415.5                       & (62.1)                                                                                                                                                                                                                       & 3419.3                                                   & (37.0)    & {[}-52.6, 45.0{]}         & 23.1     & 0.5     \\
\bottomrule
\end{tabular}}

@@

% \newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
% \begin{table}[tb]
%   \caption{Mean fitness (and standard deviation) of the best solution found. % at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. 
%   Mean runtime is shown in hours. 
%   %CEGO runs were stopped after 144 hours. This was the case for all LOP instances.
%   \label{tab:results}}
%   \resizebox{\textwidth}{!}{%
% \begin{tabular}{r@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}
%  \toprule
%             &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
%             \bf Problem & \bf     Instance & \mcolc{2}{CEGO} & \mcolc{2}{UMM}   &                         &            & \bf & \bf CEGO       & \bf UMM                       \\\midrule
% LOP
% & N-p50-01       & 21034.3             & (183.9)            & 21161.8            & (657.4)           & [-606.0,             & 351.0]              & 305.8        & 144.6 & 0.5  \\
% & N-p50-02       & 21767.3             & (254.9)            & 21746.6            & (645.4)           & [-458.6,             & 500.0]              & 315.1        & 144.5 & 0.5  \\
% & N-t1d100.01    & 78012.0             & (432.1)            & 76499.3            & (1099.7)          & [696.4,              & 2329.0]             & 158.3        & 145.1 & 1.9  \\
% & N-t1d100.02    & 78834.0             & (477.8)            & 76860.7            & (864.0)           & [1303.8,             & 2642.8]             & 156.0        & 144.7 & 1.8  \\
% & N-atp111       & 668.5               & (9.4)              & 596.6              & (17.0)            & [58.8,               & 85.0]               & 137.9        & 145.1 & 2.3  \\
% & N-atp134       & 856.4               & (12.2)             & 760.1              & (23.4)            & [78.4,               & 114.2]              & 116.5        & 145.0 & 3.3  \\
% & N-t1d150.01    & 186969.0            & (2094.6)           & 179615.6           & (1731.5)          & [5543.3,             & 9163.5]             & 103.9        & 145.7 & 4.4  \\
% & N-t1d150.02    & 183414.7            & (779.2)            & 177524.2           & (1165.6)          & [4949.2,             & 6831.8]             & 103.6        & 145.3 & 4.6  \\
% & N-t2d150.01    & 22207.3             & (1667.3)           & 15136.9            & (745.9)           & [5817.1,             & 8323.7]             & 104.5        & 145.5 & 4.5  \\
% & N-t2d150.02    & 22036.0             & (744.7)            & 14718.4            & (677.5)           & [6648.3,             & 7986.9]             & 103.1        & 145.0 & 4.5  \\
% & N-t1d200.01    & 333804.1            & (1191.9)           & 323501.4           & (1385.7)          & [9086.4,             & 11519.0]            & 77.7         & 145.4 & 7.6  \\
% & N-t1d200.02    & 331730.9            & (2819.7)           & 319786.2           & (2265.6)          & [9533.6,             & 14355.8]            & 78.2         & 145.9 & 7.1  \\
% & N-t2d200.01    & 54043.6             & (1477.6)           & 33389.0            & (1984.0)          & [19001.4,            & 22307.8]            & 78.2         & 146.7 & 7.4  \\
% & N-t2d200.02    & 52787.0             & (4194.2)           & 35589.0            & (2319.6)          & [13948.0,            & 20448.0]            & 78.9         & 145.7 & 7.5  \\
% & N-be75np\_150  & 3669753.9           & (74292.3)          & 3216907.1          & (72239.3)         & [383998.5,           & 521695.1]           & 105.2        & 145.5 & 4.4  \\
% & N-be75np\_250  & 10818828.5          & (127722.3)         & 9582261.7          & (258176.8)        & [1040022.9,          & 1433110.7]          & 62.5         & 146.4 & 12.5 \\
% & N-be75eec\_150 & 1592220.8           & (29945.9)          & 1418578.9          & (56557.7)         & [130141.0,           & 217142.8]           & 103.2        & 145.9 & 4.4  \\
% & N-be75eec\_250 & 5098734.4           & (172874.0)         & 4430408.5          & (110233.0)        & [530352.4,           & 806299.4]           & 63.0         & 146.7 & 12.3 \\\midrule
% PFSP
% & rec05          & 1317.9              & (25.1)             & 1332.5             & (15.6)            & [-34.5,              & 5.3]                & 400.0        & 38.6  & 0.1  \\
% & rec13          & 2128.2              & (25.0)             & 2163.6             & (28.1)            & [-60.4,              & -10.4]              & 400.0        & 38.6  & 0.1  \\
% & rec19          & 2398.6              & (19.8)             & 2405.2             & (12.8)            & [-22.5,              & 9.3]                & 400.0        & 85.2  & 0.2  \\\midrule
% QAP
% & nug12          & 624.2               & (26.3)             & 661.2              & (17.8)            & [-58.3,              & -15.7]              & 400.0        & 14.2  & 0.0  \\
% & kra30b         & 120192.0            & (1778.1)           & 119923.0           & (3459.6)          & [-2379.5,            & 2917.5]             & 400.0        & 85.1  & 0.2  \\
% & tho30          & 192416.0            & (2584.2)           & 191586.4           & (4342.0)          & [-2582.9,            & 4242.1]             & 400.0        & 85.6  & 0.2  \\
% & kra30a         & 119872.0            & (1746.7)           & 119502.0           & (1827.5)          & [-1309.8,            & 2049.8]             & 400.0        & 86.1  & 0.2  \\
% & nug30          & 7486.8              & (40.4)             & 7472.4             & (83.6)            & [-49.0,              & 77.8]               & 400.0        & 86.5  & 0.2  \\
% & kra32          & 115907.0            & (4663.4)           & 116898.0           & (4343.1)          & [-5226.3,            & 3244.3]             & 400.0        & 94.0  & 0.2  \\
% \bottomrule
% \end{tabular}}
% \vspace*{-1em}
%  \end{table}
